Trauma treatment delay

### 2023-12-20 manuscriptlongversion.Rmd
text

---
title: "Trauma treatment delay"
author: "Anton Wasielewski"
subtitle: A retrospective cohort study on the factors affecting the delays in trauma
  care
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
bibliography: bibliography.bib
csl: vancouver.csl
editor_options:
  markdown:
    wrap: 72
---

@@

Further analysing the results and its clinical applications, the results
can be interpreted as that it is mostly injured patients with affected
consciousness that receive delayed treatment. The clinical applications
of this can be seen as we need to do more to avoid this delay for this
patient group. The study highlights the urgency in these patients and
the heightened risk for delay they face due to their situation. If
clinicians are aware that these patients receive delayed treatment more
frequently, active steps can be taken towards reducing this risk and
bettering the trauma care.

Further applying the study clinically, it is also important to educate
clinicians on what steps went wrong in these patients. If clinicians
know the most common mistakes made in this patient group, they might be
less likely to make these mistakes themselves, possibly lowering the
risk of receiving delayed treatment for these patients with these
factors. The results of this study and similar ones should be
communicated to trauma centers, as the goal is to always better the
trauma care for patients.

>>>>

---
title: "Trauma treatment delay"
author: "Anton Wasielewski"
subtitle: A retrospective cohort study on the factors affecting the delays in trauma
  care
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
bibliography: bibliography.bib
csl: vancouver.csl
editor_options:
  markdown:
    wrap: 72
---

@@

Further analysing the results and its clinical applications, the results
can be interpreted as that it is mostly injured patients with affected
consciousness that receive delayed treatment. The clinical applications
of this can be seen as we need to do more to avoid this delay for this
patient group. It is important to remember that the delays are all
patients that have received adverse outcomes because of their delay.
Some might include injuries being missed or not being treated. The study
highlights the urgency in these patients and the heightened risk for
delay they face due to their situation. If clinicians are aware that
these patient factors receive delayed treatment more frequently, active
steps can be taken towards reducing this risk and bettering the trauma
care.

This also highlights the importance of adequate diagnostic imaging when
the patient is stabilised. It occurs that patients are stabilised in the
operating room (OR), gets taken to the CT then back to the OR. This is
important as to not miss any injury, especially in severely injured
patients where it can be difficult to identify all injuries without
diagnostic imaging. When clinicians have access to these instruments
they should be used whenever deemed necessary, as studies suggest it has
a positive effect on patient outcome [@Hajibandeh_2014].

Further applying the study clinically, it is also important to educate
clinicians on what steps went wrong in these patients and what could
have been done to prevent it. If clinicians know the most common
mistakes made in this patient group, they might be less likely to make
these mistakes themselves, possibly lowering the risk of receiving
delayed treatment for these patients with these factors. The results of
this study and similar ones should be communicated to trauma centers, as
the goal is to always better the trauma care for patients.
